A thermodynamic view of dusty protoplanetary disks: axisymmetric stability

### 2016-08-20 summary.tex
edited summary

\section{Summary}\label{summary}
In this paper we highlight the similarity between an isothermal 
dusty gas and an adiabatic, pure gas. The correspondence arises
because drag forces reduce the relative velocity between gas and
dust. In the limit of perfect dust-gas coupling, $tstop \to 0$,  
 dust is entrained in 
the gas, and $\rhod/\rhog$ is conserved following the dusty flow. 
This is analogous to entropy being conserved following a adiabatic,
pure gas.

@@

We obtain the Solberg-Hoiland criteria to assess 
axisymmetric stability when the equation of state is strictly
isothermal. We show that {\bf dust settling, by itself, cannot lead to
  axisymmetric instability, however large the associated vertical
  shear} \citep[cf. \emph{non-axisymmetric} Kelvin-Helmholtz instabilities
  in dusty disks][]{lee10}. We show that
sharp edges in the dust-to-gas ratio cannot persist in protoplanetary
disks, as these imply a sharp entropy gradient and may thus destablize
the disk.

>>>>

\section{Summary}\label{summary}
In this paper we highlight the similarity between an isothermal 
dusty gas and an adiabatic, pure gas. The correspondence arises
because drag forces reduce the relative velocity between gas and
dust. In the limit of perfect dust-gas coupling, $\tstop \to 0$,  
 dust is entrained in 
the gas, and $\rhod/\rhog$ is conserved following the dusty flow. 
This is analogous to entropy being conserved following a adiabatic,
pure gas.

@@

We obtain the Solberg-Hoiland criteria to assess 
axisymmetric stability when the equation of state is strictly
isothermal. We show that {\bf dust settling, in itself, cannot lead to
  axisymmetric instability, however large the associated vertical
  shear} \citep[cf. \emph{non-axisymmetric} Kelvin-Helmholtz instabilities
  in dusty disks][]{lee10}. We show that
sharp edges in the dust-to-gas ratio cannot persist in protoplanetary
disks, as these imply a sharp entropy gradient and may thus destablize
the disk.
